---
title: "AS3-2: 股市動態"
author: "第 1 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

```{r}
IBM = read.csv("data/IBMStock.csv")
GE = read.csv("data/GEStock.csv")
ProcterGamble = read.csv("data/ProcterGambleStock.csv")
CocaCola = read.csv("data/CocaColaStock.csv")
Boeing = read.csv("data/BoeingStock.csv")
```
+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>



###  Section-1 Summary Statistics
```{r}
library(lubridate)
#載入套件(lubridate)
```

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
dim(IBM)
dim(GE)
dim(ProcterGamble)
dim(CocaCola)
dim(Boeing)
#使用dim找出行和列的個數
```
Ans: 480個


__§ 1.2__ What is the earliest year in our datasets?
```{r}
#在資料集中最早的年份是?

IBM$Date = as.Date(IBM$Date, "%m/%d/%y")
GE$Date = as.Date(GE$Date, "%m/%d/%y")
CocaCola$Date = as.Date(CocaCola$Date, "%m/%d/%y")
ProcterGamble$Date = as.Date(ProcterGamble$Date, "%m/%d/%y")
Boeing$Date = as.Date(Boeing$Date, "%m/%d/%y")
#先將五間公司的時間格式整理一下
IBM$Date[1]
GE$Date[1]
CocaCola$Date[1]
ProcterGamble$Date[1]
Boeing$Date[1]
#找出最早的時間，這個資料的時間原本就有按照時間排序了，如果沒有應該要先排序

```
Ans: 1970年
__§ 1.3__ What is the latest year in our datasets?
```{r}
IBM$Date[480]
#在資料集中最晚的年份是?

```
Ans: 2009年

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
mean(IBM$StockPrice)
#將IBM股價取平均
#
```
Ans: 144.4

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
min(GE$StockPrice)
#找出GE的最低股價
#
```

Ans: 9.294

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
max(CocaCola$StockPrice)
#找出CocaCola的最高股價
#
```
Ans: 146.6

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
median(Boeing$StockPrice)
#找出Boeing股價的中位數
#
```
Ans: 44.88

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
sd(ProcterGamble$StockPrice)
#寶潔公司股票在這段時間內的標準差是多少？
#
```
Ans: 18.19

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
CocaCola_ts = as.POSIXct(CocaCola$Date, format="%m/%d/%y")

year(CocaCola_ts[which.max(CocaCola$StockPrice)])
#找出可口可樂股價最高的年份

year(CocaCola_ts[which.min(CocaCola$StockPrice)])
#找出可口可樂股價最低的年份

plot(CocaCola$Date, CocaCola$StockPrice, type="l")
#畫出可口可樂的時間股價圖
```
Ans:最高是1973年，最低是1980年

__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
#2000年3月，技術泡沫破滅，股市崩盤。 根據這個情節，哪家公司的股票跌幅更大？

plot(CocaCola$Date, CocaCola$StockPrice, type="l", col="Red")
lines(ProcterGamble$Date, ProcterGamble$StockPrice, col="Blue", lty=2)
#先以紅線畫出CocaCola股價趨勢圖，再以藍虛線畫出ProcterGamble的
abline(v=as.Date(c("2000-03-01")), lwd=2)
#再2000/03/01的地方畫黑線以利查看
```

Ans:寶潔公司

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
#（a）1983年左右，其中一家公司（可口可樂或寶潔公司）的股票上漲，而另一家則下跌。 哪一個上升？
plot(CocaCola$Date, CocaCola$StockPrice, type="l", col="Red")
lines(ProcterGamble$Date, ProcterGamble$StockPrice, col="Blue", lty=2)

abline(v=as.Date(c("1983-01-01")), lwd=2)
#同上題，在1983/01/01的地方畫黑線以利查看趨勢
```
Ans:寶潔公司下降，可口可樂則上升。


(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
#在圖中顯示的時間段內，哪種股票的價值通常較低？
#同上圖可以看到紅線通常比較低
```
Ans:可口可樂

<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
#2000年3月科技泡沫破滅後，哪種股票跌幅最大？
plot(CocaCola$Date[301:432], CocaCola$StockPrice[301:432], type="l",col="red", ylim=c(0,210))
#先畫出CocaCola的在1995到2005間的股價趨勢圖，Y軸上限設定為210

lines(ProcterGamble$Date[301:432], ProcterGamble$StockPrice[301:432], col="blue")
lines(IBM$Date[301:432], IBM$StockPrice[301:432], col="green")
lines(GE$Date[301:432], GE$StockPrice[301:432], col="orange")
lines(Boeing$Date[301:432], Boeing$StockPrice[301:432], col="black")
#接著分別以藍、綠、橘、黑線畫出ProcterGamble、IBM、GE、Boeing的趨勢圖
abline(v=as.Date(c("2000-03-01")), lwd=2)
#最後在2000/03/01的地方畫黑線以利觀察，得知GE跌幅最大
```
Ans: GE


__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
#在1995-2005年期間哪種股票達到最高值？
#直接看上圖，我們可以看到綠線(IBM)有最高值。
```
Ans:IBM

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
#1997年10月，全球股市崩盤是由亞洲經濟危機引發的。 比較1997年9月至1997年11月，哪些公司的股價下跌趨勢？
plot(CocaCola$Date[301:432], CocaCola$StockPrice[301:432], type="l", col="red", ylim=c(0,210))
lines(ProcterGamble$Date[301:432], ProcterGamble$StockPrice[301:432], col="blue")
lines(IBM$Date[301:432], IBM$StockPrice[301:432], col="green")
lines(GE$Date[301:432], GE$StockPrice[301:432], col="orange")
lines(Boeing$Date[301:432], Boeing$StockPrice[301:432], col="black")
#同上，畫出五家公司的股價趨勢圖
abline(v=as.Date(c("1997-09-01","1997-11-01")), lwd=2)
#然後在1997年的9月到11月間畫黑線，我們就可以看到ProcterGamble & Boeing 走下坡。

```
Ans: ProcterGamble & Boeing 

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
#在這個時期（2004年和2005年）的最後兩年，哪些股票似乎表現最好，就股價上漲而言？
plot(CocaCola$Date[301:432], CocaCola$StockPrice[301:432], type="l", col="red", ylim=c(0,210))
lines(ProcterGamble$Date[301:432], ProcterGamble$StockPrice[301:432], col="blue")
lines(IBM$Date[301:432], IBM$StockPrice[301:432], col="green")
lines(GE$Date[301:432], GE$StockPrice[301:432], col="orange")
lines(Boeing$Date[301:432], Boeing$StockPrice[301:432], col="black")
#同上，畫出五家公司的股價趨勢圖
abline(v=as.Date(c("2004-01-01","2005-01-01")), lwd=2)
#然後分別在2004年和2005年畫黑線，可以看到黑線(Boeing)持續上漲。
```
Ans: Boeing

<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
#對於IBM，將月平均值與總體平均股票價格進行比較。 IBM歷史上哪些月有高股票價格（平均）？ 選擇所有符合條件的。
mean(IBM$StockPrice)
#先求IBM股價的平均值
tapply(IBM$StockPrice, months(IBM$Date), mean) %>% sort
#再以月份查看股價的平均值再由小到大排序，大於平均值即是。
```
Ans: 一月到五月都是

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
#GE和CocaCola在某一個月的平均股價最高。 這是哪個月？
mean(GE$StockPrice)
mean(CocaCola$StockPrice)
#先找出GE和CocaCola的平均股價
tapply(GE$StockPrice, months(GE$Date), mean) %>% sort
tapply(CocaCola$StockPrice, months(CocaCola$Date), mean) %>% sort
#再以月份查看股價的平均值再由小到大排序，可以看到四月是最高的。
```
Ans: 四月

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
#比較12月和1月份，每家公司的平均股價在一個月內較高而在另一個月較低。 而是哪個月股價下跌？
tapply(GE$StockPrice, months(GE$Date), mean) %>% sort
tapply(CocaCola$StockPrice, months(CocaCola$Date), mean) %>% sort
tapply(Boeing$StockPrice, months(Boeing$Date), mean) %>% sort
tapply(ProcterGamble$StockPrice, months(ProcterGamble$Date), mean) %>% sort
tapply(IBM$StockPrice, months(IBM$Date), mean) %>% sort
#將每家公司的每月平均股價由小到大列表，可以發現十二月都在一月的前面。
#
```
Ans: 十二月

<br><br><br>

