---
title: "AS3-1: 數位偵探"
author: "第 1 組"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=F}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr, d3heatmap)
```
<hr>

犯罪是一個國際關注的問題，但它在不同的國家以不同的方式記錄和處理。 在美國，聯邦調查局（FBI）記錄了暴力犯罪和財產犯罪。 此外，每個城市都記錄了犯罪行為，一些城市發布了有關犯罪率的數據。 伊利諾伊州芝加哥市從2001年開始在線發布犯罪數據。

芝加哥是美國人口第三多的城市，人口超過270萬。在這個作業裡面，我們將關注一種特定類型的財產犯罪，稱為「汽車盜竊」，我們將使用R中的一些基本數據分析來了解芝加哥的汽車盜竊紀錄。請載入文件"data/mvtWeek1.csv"：以下是各欄位的描述：

+ `ID`: a unique identifier for each observation
+ `Date`: the date the crime occurred
+ `LocationDescription`: the location where the crime occurred
+ `Arrest`: whether or not an arrest was made for the crime (TRUE if an arrest was made, and FALSE if an arrest was not made)
+ `Domestic`: whether or not the crime was a domestic crime, meaning that it was committed against a family member (TRUE if it was domestic, and FALSE if it was not domestic)
+ `Beat`: the area, or "beat" in which the crime occurred. This is the smallest regional division defined by the Chicago police department.
+ `District`: the police district in which the crime occured. Each district is composed of many beats, and are defined by the Chicago Police Department.
+ `CommunityArea`: the community area in which the crime occurred. Since the 1920s, Chicago has been divided into what are called "community areas", of which there are now 77. The community areas were devised in an attempt to create socially homogeneous regions.
+ `Year`: the year in which the crime occurred.
+ `Latitude`: the latitude of the location at which the crime occurred.
+ `Longitude`: the longitude of the location at which the crime occurred.

<br>

- - -
```{r results='hide',message=FALSE}
library(dplyr)
library(lubridate)
library(d3heatmap)
library(ggplot2)
```


###  Section-1 Loading the Data

【1.1】How many rows of data (observations) are in this dataset?
```{r}
# Load Datasets
mvt <- read.csv("data/mvtWeek1.csv", header = T, stringsAsFactors = F)
# 用nrow即可知道rows of data是多少，此dataset為191641
nrow(mvt)
```

檢查各欄位的資料格式
```{r}
# 用str可知道各欄位的資料格式與蓋要值
str(mvt)
```

類別(Factor) versus 字串(Character)

【1.2】How many variables are in this dataset?
```{r}
# 用ncol即可知道variables有多少，這dataset有11個variables
# 抑或是用str的第一行可知道observations & variables
ncol(mvt)
```
__Ans:__ 11

【1.3】Using the "max" function, what is the maximum value of the variable "ID"?
```{r}
# max function finds the maximum value of the variable "ID" is 9181151
max(mvt$ID)
```
__Ans:__ 9181151

【1.4】 What is the minimum value of the variable "Beat"?
```{r}
min(mvt$Beat)
```
__Ans:__ 111

【1.5】 How many observations have value TRUE in the Arrest variable (this is the number of crimes for which an arrest was made)?
```{r}
# 因為TRUE值為1; FALSE值為0，運用sum加總起來可知TRUE的個數
sum(mvt$Arrest)
```
__Ans:__ 15536
【1.6】 How many observations have a LocationDescription value of ALLEY?
```{r}
# 用dplyr 選mvt操作先filter出LocationDescription等於ALLEY，再用nrow算出observations之值
mvt %>% 
  filter(LocationDescription == "ALLEY") %>% 
  nrow()
```
__Ans:__ 2308

<br><br>

- - -

### Section-2 Understanding Dates in R

【2.1】 In what format are the entries in the variable Date?

+ Month/Day/Year Hour:Minute
+ Day/Month/Year Hour:Minute
+ Hour:Minute Month/Day/Year
+ Hour:Minute Day/Month/Year

```{r}
# 用head看Date資料格式長怎樣
head(mvt$Date)
```
__Ans:__ 格式是 Month/Day/Year Hour:Minute

### 格式轉換 Character -> Date 和新增Month及Weekday
```{r}
DateConvert <- as.Date(strptime(mvt$Date, "%m/%d/%y %H:%M"))
summary(DateConvert)
mvt$Month <- months(DateConvert)
mvt$Weekday <- weekdays(DateConvert)
mvt$Date <- DateConvert
```

```{r}
table(format(DateConvert,'%w'))
table(format(DateConvert,'%m'))
table(weekday=format(DateConvert,'%w'), month=format(DateConvert,'%m'))
```

#### （不確定）
```{r fig.height=2.5, fig.width=8}
par(cex = 0.7)
hist(DateConvert,"year",las=2,freq=T,xlab="")
table(format(DateConvert, "%u"), format(DateConvert, "%H")) %>% 
  as.data.frame.matrix() %>% 
  d3heatmap(F, F, col = colorRamp(c('seagreen','lightyellow','red')))
```


【2.2】 What is the month and year of the median date in our dataset? 
```{r}
# 直接取Date的median
median(mvt$Date)
```
__Ans:__ 2006年5月

【2.3】 In which month did the fewest motor vehicle thefts occur?
```{r}
# 直接利用先前新增的Month變數，用table計算各月的竊盜次數並遞增排序
mvt$Month %>% 
  table() %>% 
  sort()
```
__Ans:__ 由上表可知，2月 13511次是最少發生竊盜的月份

【2.4】 On which weekday did the most motor vehicle thefts occur?
```{r}
# 直接利用先前新增的Weekday變數，用table計算各週的竊盜次數並遞增排序
mvt$Weekday %>% 
  table() %>% 
  sort()
```
__Ans:__ 由上表可知，週五 29284次是最多發生竊盜的Weekday

【2.5】 Which month has the largest number of motor vehicle thefts for which an arrest was made?
```{r}
mvt$Month[mvt$Arrest] %>% table() %>% sort()
```
__Ans:__ 由上表可知，1月 1435次是最多被逮捕的月份

<br><br>

- - -

### Section-3 Visualizing Crime Trends

【3.1】 (a) In general, does it look like crime increases or decreases from 2002 - 2012? (b) In general, does it look like crime increases or decreases from 2005 - 2008? (c) In general, does it look like crime increases or decreases from 2009 - 2011?
```{r}
plotCrime <- as.data.frame(table(mvt$Year))
colnames(plotCrime) <- c("Year", "CrimeFreq")

# 用ggplot2的qplot快速畫出年跟犯罪次數的折線圖
qplot(Year, CrimeFreq, group = 1, data = plotCrime, geom = "line")
```
__Ans:__ <br>
(a) 由上圖可知2002-2012年整體犯罪次數是*下降*的(decrease)
(b) 由上圖可知2005-2008年整體犯罪次數是*下降*的(decrease)
(c) 由上圖可知2009-2011年整體犯罪次數是*上升*的(increase)

【3.2】 Does it look like there were more crimes for which arrests were made in the first half of the time period or the second half of the time period?
```{r}
summary(mvt$Date)
```

【3.3】 For what proportion of motor vehicle thefts in 2001 was an arrest made?
```{r}
table(mvt$Arrest, mvt$Year) %>%
  prop.table(2) %>% 
  round(3)
# 0.104
```
__Ans:__ 0.104

【3.4】 For what proportion of motor vehicle thefts in 2007 was an arrest made?
```{r}
table(mvt$Arrest, mvt$Year) %>%
  prop.table(2) %>% 
  round(3)
```
__Ans:__ 0.085


【3.5】 For what proportion of motor vehicle thefts in 2012 was an arrest made?
```{r}
table(mvt$Arrest, mvt$Year) %>%
  prop.table(2) %>% 
  round(3)
```
__Ans:__ 0.039

<br><br>

- - -

### Section-4 Popular Locations

【4.1】 Which locations are the top five locations for motor vehicle thefts, excluding the "Other" category? You should select 5 of the following options.

```{r}
table(mvt$LocationDescription) %>% 
  sort() %>% 
  tail(6)
```

【4.2】 How many observations are in Top5?
```{r}
(top5 = names(table(mvt$LocationDescription) %>% sort %>% tail(6))[-4])

sum(mvt$LocationDescription %in% top5)  # 177510
```

【4.3】 One of the locations has a much higher arrest rate than the other locations. Which is it? 
```{r}
TOP5 = subset(mvt, LocationDescription %in% top5)
tapply(TOP5$Arrest, TOP5$LocationDescription, mean) %>% sort
```

【4.4】 On which day of the week do the most motor vehicle thefts at gas stations happen?
```{r}
DateConvert[mvt$Location == "GAS STATION"] %>% 
  format('%w') %>% table %>% sort
```

【4.5】 On which day of the week do the fewest motor vehicle thefts in residential driveways happen?
```{r}
DateConvert[mvt$Location == "DRIVEWAY - RESIDENTIAL"] %>% 
  format('%w') %>% table %>% sort
```


<br><br><br>


