---
title: "U2.AS2: 股市動態"
author: "第 0 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: ../style.css
---

<br><hr>

基本的程式筆記設定
```{r results='hide', message=FALSE, warning=FALSE}
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
```

安裝、載入一些基本的套件
```{r results='hide', message=FALSE, warning=FALSE}
if(!require(devtools)) install.packages("devtools")
if(!require(devtools)) devtools::install_github("hadley/emo")
if(!require(pacman)) install.packages("pacman")
pacman::p_load(magrittr, dplyr)
```

- - -

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
IBM = read.csv("data/IBMStock.csv")
GE = read.csv("data/GEStock.csv")
PG = read.csv("data/ProcterGambleStock.csv")
CK = read.csv("data/CocaColaStock.csv")
BE = read.csv("data/BoeingStock.csv")
IBM$Date = as.Date(IBM$Date, "%m/%d/%y")
GE$Date = as.Date(GE$Date, "%m/%d/%y")
CK$Date = as.Date(CK$Date, "%m/%d/%y")
PG$Date = as.Date(PG$Date, "%m/%d/%y")
BE$Date = as.Date(BE$Date, "%m/%d/%y")

str(IBM)
nrow(IBM)
```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
min(IBM$Date)
```

__§ 1.3__ What is the latest year in our datasets?
```{r}
max(IBM$Date)
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
mean(IBM$StockPrice)
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
min(GE$StockPrice)
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
max(CK$StockPrice)
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
median(BE$StockPrice)
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
sd(PG$StockPrice)
```

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
plot(CK$Date, CK$StockPrice, type='l')  # 1973 1980
abline(v=CK$Date[which.max(CK$StockPrice)], col='green')
abline(v=CK$Date[which.min(CK$StockPrice)], col='red')
```


__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
plot(CK$Date, CK$StockPrice, type='l', col='blue', lwd=2)
lines(PG$Date, PG$StockPrice, col="green", lwd=2)
abline(v = as.Date("2000-03-01"), lty=3, col='orange')
abline(v = as.Date("1983-07-01"), lty=3, col='orange')
legend("topright",legend=c("Coke","P&G"),col=c('blue','green'),lwd=2)

```

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
# Coca-Cola
```

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
# Coca-Cola
```


<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
plot(CK$Date[301:432], CK$StockPrice[301:432], 
     type="l", col="red", ylim=c(0,210))
lines(PG$Date[301:432],  PG$StockPrice[301:432],  col="blue")
lines(IBM$Date[301:432], IBM$StockPrice[301:432], col="green")
lines(GE$Date[301:432],  GE$StockPrice[301:432],  col="purple")
lines(BE$Date[301:432],  BE$StockPrice[301:432],  col="orange")
abline(v = as.Date("2000-03-01"), lty=3, col='gray')
abline(v = as.Date("1997-09-01"), lty=3, col='gray')
abline(v = as.Date("1997-11-01"), lty=3, col='gray')

```

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
# IBM
```

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
# P&G and Boeing
```

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
# Boeing
```


<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
tapply(IBM$Stock, format(IBM$Date,"%m"), mean) - mean(IBM$Stock)
```

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
sapply(list(BE=BE,CK=CK,GE=GE,IBM=IBM,PG=PG), function(df) {
  tapply(df$Stock, format(df$Date,"%m"), mean) - mean(df$Stock)
  })  # April
```

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
# December
```


